\section{Generality across one-parameter min-max settings}
\label{sec:integration-generality}

The combinatorial step formalized here is not specific to the
closed-minimal-hypersurface setting of~\cite{DLT13}. Recall the
shape of the $1$-parameter Almgren--Pitts pattern: a continuous
family of sweepouts indexed by $t \in [0,1]$, a scalar energy
$f(t)$ attached to each sweepout, the inf-sup level
$m_0 = \inf_{\mathcal{A}} \sup f$ over an admissible class
$\mathcal{A}$, a local replacement lemma producing a
quantitative saving on a neighborhood of each near-critical
$t$, and a combinatorial step combining these local
replacements into a competitor strictly below $m_0$. This
pattern recurs in several geometric variants beyond the
original. We mention four.

\begin{itemize}
\item \emph{Free boundary minimal hypersurfaces}~\cite{LZ21}:
  the sweepout is by free-boundary regions in a manifold with
  boundary, and the local replacement lemma uses level sets of
  the distance function to the hypersurface in place of the
  exponential-map construction of~\cite{DLT13}. The energy is
  again the boundary $\mathcal{H}^n$-area.
\item \emph{Constant mean curvature
  hypersurfaces}~\cite{ZZ19}: the energy is the
  prescribed-mean-curvature functional
  $f_\Omega = \mathcal{H}^n(\partial \Omega) - c \cdot
  \mathrm{vol}(\Omega)$, and the local replacement lemma is
  adapted to produce a quantitative saving in this functional.
\item \emph{Complete manifolds of finite
  volume}~\cite{ChL19}: the sweepout is by hypersurfaces of
  bounded volume in a complete non-compact manifold; the main
  geometric input is the disjointing lemma stating that any
  such sweepout can be made by mutually disjoint hypersurfaces
  of nearly the same volume.
\item \emph{Anisotropic min-max}~\cite{DDL24}: the area
  $\mathcal{H}^n(\partial \Omega)$ is replaced by an elliptic
  integrand $F(\partial \Omega)$; the local replacement lemma
  carries the anisotropic structure and produces an analogous
  quantitative saving.
\end{itemize}

In each case the local replacement lemma differs in substance
from the one in~\cite{DLT13}, but the subsequent combinatorial
step is the same: the interval refinement, the two-fold
overlap invariant, and the scalar bookkeeping that turns the
resulting cover into a sup-reducing competitor are all carried
out by the formalization presented here. The
\texttt{LocalWitness} structure of \S\ref{sec:integration-input}
does not depend on the geometric origin of its four data fields,
specifying only an open neighborhood, a continuous scalar
energy, and the quantitative saving inequality. Any of the
local replacement lemmas above can therefore feed the present
formalization to produce a sup-reducing competitor for the
corresponding inf-sup level, with the script of
Appendix~\ref{app:lean-script} carrying over verbatim and only
the geometric stubs (\texttt{YourGMT.*}) replaced by the
relevant variant's geometric formalization.

