\section{Lifting to a min-max proof}
\label{sec:integration}

We indicate how the formalization developed in
\S\S\ref{sec:spec}--\ref{sec:proof} fits into a complete
formalization of an Almgren--Pitts min-max construction.
Suppose the surrounding geometric and admissibility infrastructure
has been set up in Lean: an admissible class $\mathcal{A}$ of
sweepouts, the inf-sup characterization
$m_0 = \inf_{\Omega \in \mathcal{A}} \sup f_\Omega$, the local
replacement construction~\cite[Lemma~3.1]{DLT13}, and the
Hausdorff measure of boundary surfaces. The four objects
introduced in \S\ref{sec:spec},
\texttt{LocalWitness} (Definition~\ref{def:witness}),
\lean{exists\_refinement}{OneDim/Assembly.lean},
\lean{exists\_sup\_reduction\_of\_cover}{Cover.lean}, and the
chained \lean{exists\_sup\_reduction}{SupReduction.lean},
carry no geometric content. They are, respectively, the
abstract local-reducer data, \cite{DLT13}~\S3.2 Step~1
(the interval refinement to a finite cover with two-fold
overlap), \cite{DLT13}~\S3.2 Step~2 (the scalar bookkeeping
over the cover), and the chained $1$-parameter conclusion. The
same four declarations apply in both the abstract and the
instantiated form; what changes between them is only the
data passed in.

\subsection{The geometric input:
\texorpdfstring{\texttt{LocalWitness} from the local replacement lemma}{LocalWitness from the local replacement lemma}}
\label{sec:integration-input}

The \texttt{LocalWitness} structure was chosen so that its
fields match the data the local replacement
lemma~\cite[Lemma~3.1]{DLT13} produces. Fix a sweepout
$\Omega \in \mathcal{A}$ realizing $m_0 = \sup f_\Omega$ and an
integer $N \ge 1$. At every parameter $t \in [0,1]$ with
$f_\Omega(t) \ge m_0 - 1/N$, the replacement lemma supplies an
open interval $(a_t, b_t) \subseteq [0,1]$ around $t$ on which
a local replacement saves boundary energy. Recording the
interval as the \texttt{neighborhood} field, the boundary
energy of the replaced sweepout
\[
  s \;\longmapsto\; \mathcal{H}^n(\partial \widetilde{\Omega}_s),
  \qquad
  \widetilde{\Omega}_s := \text{$\Omega$ with the local
  replacement inserted at parameter $s$},
\]
as the \texttt{replacementEnergy} field, its continuity in $s$
as \texttt{replacementEnergy\_continuous}, and the quantitative
estimate
\[
  f_\Omega(s) - \mathcal{H}^n(\partial \widetilde{\Omega}_s)
  \;\ge\; \frac{1}{4N}
  \qquad \text{for } s \in (a_t, b_t)
\]
as \texttt{saving\_bound}, one obtains an instance of
\texttt{LocalWitness}\,$([0,1], f_\Omega, t, 1/(4N))$. Of these
four data items, only the continuity is treated implicitly in
the literature (through the continuity of the replaced family
in the inserted parameter); in the Lean formalization it must
be supplied explicitly.

\subsection{The chain: from sup reduction to inf-sup contradiction}
\label{sec:integration-chain}

With the per-parameter local witnesses in place, the chained
theorem \lean{exists\_sup\_reduction}{SupReduction.lean}
produces a competitor $f' : [0,1] \to \mathbb{R}$ together
with a modification set $S \subseteq [0,1]$ satisfying
\[
  \{t : f_\Omega(t) \ge m_0 - 1/N\} \subseteq S, \qquad
  f' \le f_\Omega \text{ on } [0,1], \qquad
  f' = f_\Omega \text{ on } [0,1] \setminus S,
\]
together with the supremum bound
$\sup f' \le m_0 - 1/(4N)$. This is the formalization of the
sup-reduction step in the literature argument: $f'$ is the
boundary energy of $\Omega$ after the local replacements have
been combined, and the off-$S$ agreement ensures that $f'$ is
a genuine combinatorial reduction of $f_\Omega$ rather than a
trivial constant.

The proof of the min-max theorem now closes the standard way.
The off-$S$ agreement makes the geometric lift routine: there
exists $\Omega' \in \mathcal{A}$ that agrees with $\Omega$
outside $S$ and uses the local replacement on each component
of $S$, and one checks $f' = f_{\Omega'}$. The three
inequalities
\[
  \sup f_{\Omega'} \;=\; \sup f' \;\le\; m_0 - \tfrac{1}{4N}
  \;<\; m_0 \;=\; \inf_{\mathcal{A}} \sup
\]
together with $\Omega' \in \mathcal{A}$ contradict the
inf-sup characterization of $m_0$. The first
inequality is the present formalization; the geometric lift
producing $\Omega'$ is supplied by the surrounding Lean
formalization. The full Lean script for this chain appears as
Listing~\ref{lst:end-to-end} in Appendix~\ref{app:lean-script}.


\subsection{Scope of the present formalization}
\label{sec:integration-scope}

We close with three caveats. First, the parameter space is
fixed at $[0,1]$; multi-parameter sweepouts ($[0,1]^m$, in
particular Almgren cycles) require a multi-parameter cover
construction not carried out here. Second, the output is the
scalar pair $(f', S)$, not a geometric replacement: the
construction of the sweepout $\Omega' \in \mathcal{A}$
realizing $f' = f_{\Omega'}$ falls outside the present
formalization, though the off-$S$ agreement was chosen so as
to make this lift mechanical. Third, the continuity of the
replaced family in the inserted parameter is treated
implicitly in~\cite{DLT13}; in the Lean formalization this
becomes the \texttt{replacementEnergy\_continuous} field of
\texttt{LocalWitness} and must be supplied explicitly. The
formalization itself depends only on the three standard
foundational axioms \texttt{propext}, \texttt{Classical.choice},
and \texttt{Quot.sound}; standard measure-theory work in
Mathlib stays within the same three.

